\documentclass[11pt]{article}
%	options include 12pt or 11pt or 10pt
%	classes include article, report, book, letter, thesis

\title{HW13}
\author{Shane Drafahl}
\date{16 October ,2017}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{graphics}

\begin{document}
\maketitle

1. $ G = (\{\ G,T,B,A,F \}\, \{\ 1,0 \}\ ,S,P) $
$ \newline $
$ P = \{\ $
$ \newline $
$ S \rightarrow GTB | \epsilon $
$ \newline $
$ G \rightarrow GA | GC | F $
$ \newline $
$ A1 \rightarrow 1A $
$ \newline $
$ A0 \rightarrow 0A $
$ \newline $
$ AT \rightarrow 1TA $
$ \newline $
$ C0 \rightarrow 0C $
$ \newline $
$ C1 \rightarrow 1C $
$ \newline $
$ AB \rightarrow 1B $
$ \newline $
$ CB \rightarrow 0A $
$ \newline $
$ CT \rightarrow 0TC $
$ \newline $
$ FT \rightarrow F $
$ \newline $
$ F0 \rightarrow 0F $
$ \newline $
$ F1 \rightarrow 1F $
$ \newline $
$ FB \rightarrow \epsilon $
$ \newline $

$ \}\ $

$ \newline $
2. $ L = \{\ p(M)p(w) : $ M uses a finite number of tape cells when running on input w $ \}\ $
$ \newline $
L is turring acceptable. If a machine halts accepts w and reaches the halting state it would have take finite
tape cells therefore a machine can be created to accept L.

$ \newline $
To show that L is not decidable. We will use proof by contradiction and assume L is
a decidable language. Therefore there would exist a Turring Machine $ M_{L} $ that can decide L.
We can use $ M_{L} $ as a subroutine to construct a decider for the halting problem.
Suppose we construct $ M_{k} $ that takes $ k $.

$ \newline $

$ M_{k} $ : Input $ x \in \Sigma^{*} $
$ \newline $
1. If x is not of the form $ <M,w> $ else you reject
$ \newline $
2. Run $ M_{L} $ on input x
$ \newline $
3. Accept iff $ M_{L} $ accepts

$ \newline $

Proof of Correctness:

$ \newline $

$ M(w) halts \leftrightarrow w \in L(M) $
$ \newline $
$ \leftrightarrow $ M uses a finite number of tape cells when running on w.
$ \newline $
$ \leftrightarrow M_{L} accepts <M, w> $
$ \leftrightarrow M_{K} accepts x = <M, w> $

$ \newline $

Therefore $ M_{k} $ decides the halting problem. This cannot happen because the halting problem is not decidable.
Therefore the assumption for the contradiction but be incorrect. So therefore $ M_{L}  \notin TDL $. QED

$ \newline $

Otherwise another way to prove this is the complement of L is a language where
M uses an infinite number of tape cells. This is not acceptable because this machine
can never say yes because it will be infinitely checking tape cells for a yes. Therefore
becaues the complement is not turring acceptable it cannot be decidable.

$ \newline $

$ L = \{\ p(M)p(w)01^{n}0 : $ M uses at most n tape cells when running on input w $ \}\ $

$ \newline $

This language is turring decidable. This language is acceptable because if it uses at most n tape
cells it can accept it. To prove its turring decidable we need to create a machine that can decide it. Suppse we create
this machine $ M_{L} $.

$ M_{L} $ : Input $ x \in \Sigma^{*} $
$ \newline $
1. If x is not of the form $ <M,w> $ else you reject
$ \newline $
2. Create an infinite number of tape that are coppies of w
$ \newline $
3. Change the all the transitions for M to the next piece of tape for the corresponding location in tape
$ \newline $
4. Run $ M_{L} on w $ and count the number of tape cells it uses. Reject if it uses more than n cells.
$ \newline $
5. Accept iff there are less than n tape cells marked.

$ \newline $

Everytime $ M_{L} $ moves the head it transitions to a new peice of tape. In otherwords if the head moves back and forth
the head will transition to an identical peice of tape so whenever it transitions it will use a peice of tape even if it does not halt
and loops over y tape cells. If this machine does not halt but does not loop over a finite number of cells it will also end up using
more than n cells as soon as it reaches over n cells. Therefore L is decidable.

\end{document}
